Constraining the Interiors of Asteroids Through Close Encounters

### 2022-03-29 paper/main.tex
Ready to rerun blob

\begin{figure}
  \centering
  \includegraphics[height=0.89\textheight]{figs/scan-vex.pdf}
  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of orbital excess velocity $v_\infty$. The vertical dashed line indicates the reference asteroid value.}
  \label{fig:scan-vex}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[height=0.89\textheight]{figs/scan-perigee.pdf}
  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of perigee distance $r_p$. The vertical dashed line indicates the reference asteroid value. The dotted curve indicates a power-law fit (see text).}
  \label{fig:scan-perigee}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[height=0.89\textheight]{figs/scan-product.pdf}
  \caption{1- and 2-$\sigma$ confidence intervals divided by $\sigma_\theta$ for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty product $\sigma_\theta \sigma_\rho$. The vertical dashed line indicates the reference asteroid value.}
  \label{fig:scan-product}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[height=0.89\textheight]{figs/scan-vex.pdf}
  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of orbital excess velocity $v_\infty$. The vertical dashed line indicates the reference asteroid value of 6 km s$^{-1}$.}
  \label{fig:scan-vex}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[height=0.89\textheight]{figs/scan-perigee.pdf}
  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of perigee distance $r_p$. The vertical dashed line indicates the reference asteroid value of 5 Earth radii. The dotted curve indicates a power-law fit (see text).}
  \label{fig:scan-perigee}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[height=0.89\textheight]{figs/scan-product.pdf}
  \caption{1- and 2-$\sigma$ confidence intervals divided by $\sigma_\theta$ for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty product $\sigma_\theta \sigma_\rho$. The vertical dashed line indicates the reference asteroid value of $10^{-7}$.}
  \label{fig:scan-product}
\end{figure}
